---
title: "SIMULATED-TORIVUMAB-2026 | Annotated CRF | FICTIONAL — NOT FOR REGULATORY USE"
subtitle: |
  Protocol: TORIVA-LUNG 301 | Phase 3 NSCLC | Version 1.0
  CDASH v2.1 \u2192 SDTMIG v3.4 \u2192 ADaMIG v1.3 | CDISC CT 2024-03 | MedDRA v27.0 | CTCAE v5.0
author: "Prepared by: Nova (AI Clinical Data Science Assistant) | Review: Lovemore Gakava"
date: "`r format(Sys.Date(), '%Y-%m-%d')`"
output:
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true
    theme: flatly
    highlight: tango
    self_contained: true
  pdf_document:
    toc: true
    toc_depth: 3
    latex_engine: xelatex
    number_sections: false
    df_print: kable
geometry: "margin=1.5cm"
fontsize: 10pt
header-includes:
  - \usepackage{xcolor}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{colortbl}
  - \usepackage{fontspec}
  - \definecolor{sdtmred}{HTML}{C00000}
  - \definecolor{rowgray}{HTML}{EBF3FB}
---

```{r setup, include=FALSE}
# torivumab guidelines loaded
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(dplyr)
library(knitr)
library(kableExtra)
library(readr)

# Read field definitions (relative path — must knit from crf/ directory or set working dir)
fields <- read_csv("field_definitions.csv", show_col_types = FALSE) %>%
  mutate(
    codelist_name  = ifelse(is.na(codelist_name) | codelist_name == "", "\u2014", codelist_name),
    required       = ifelse(required == "Yes", "Y", ifelse(required == "No", "N", required))
  )

# Helper: build SDTM annotation string
make_annot <- function(sdtm_domain, sdtm_variable, codelist_name) {
  base  <- paste0("\u2192 ", sdtm_domain, ".", sdtm_variable)
  cl    <- ifelse(codelist_name != "\u2014", paste0(" [", codelist_name, "]"), "")
  paste0(base, cl)
}

# Hex-color row_spec is HTML-only; LaTeX chokes on bare # characters
html_row_spec <- function(tbl, ...) {
  if (knitr::is_html_output()) tbl %>% row_spec(...) else tbl
}

# Helper: render a form table with SDTM annotation column styled in red
render_form <- function(domain, fname = NULL) {
  df <- fields %>% filter(form_domain == domain)
  if (!is.null(fname)) df <- df %>% filter(form_name == fname)

  df <- df %>%
    mutate(
      n      = row_number(),
      annot  = make_annot(sdtm_domain, sdtm_variable, codelist_name)
    ) %>%
    select(n, cdash_variable, field_label, data_type, codelist_name, required, annot)

  is_html <- knitr::is_html_output()

  tbl <- df %>%
    kbl(
      col.names = c("#", "CDASH Variable", "Field Label", "Data Type",
                    "Codelist", "Req", "SDTM Annotation"),
      escape    = TRUE,
      booktabs  = TRUE,
      align     = c("c", "l", "l", "l", "l", "c", "l")
    ) %>%
    kable_styling(
      bootstrap_options = c("striped", "hover", "condensed", "responsive"),
      latex_options     = c("striped", "hold_position"),
      full_width        = TRUE,
      font_size         = 11
    )

  if (is_html) {
    tbl <- tbl %>%
      column_spec(7, color = "#C00000", bold = TRUE, italic = TRUE, width = "18em") %>%
      column_spec(6, bold = TRUE, width = "3em") %>%
      html_row_spec(0, background = "#1F3864", color = "white", bold = TRUE)
  } else {
    tbl <- tbl %>%
      column_spec(7, color = "sdtmred", bold = TRUE, italic = TRUE) %>%
      column_spec(6, bold = TRUE)
  }

  tbl
}
```

```{css, echo=FALSE}
body { font-family: Calibri, Arial, sans-serif; font-size: 13px; color: #222; }
h1 { background: #1F3864; color: white; padding: 10px 14px; border-radius: 4px; }
h2 { background: #2E75B6; color: white; padding: 8px 12px; border-radius: 4px; }
h3 { background: #41719C; color: white; padding: 6px 10px; border-radius: 3px; }
.warn  { background: #FFF2CC; border: 2px solid #C00000; padding: 12px; border-radius: 4px;
          margin-bottom: 16px; color: #C00000; font-weight: bold; }
.info  { background: #DEEAF1; border-left: 4px solid #2E75B6; padding: 10px 14px; margin-bottom: 12px; }
.recist { background: #E2EFDA; border-left: 4px solid #375623; padding: 10px 14px; margin-bottom: 12px;
           font-size: 12px; }
table  { border-collapse: collapse; width: 100%; margin-bottom: 16px; font-size: 12px; }
th     { background: #1F3864; color: white; padding: 8px 10px; text-align: left; }
td     { padding: 6px 10px; border-bottom: 1px solid #D9E1F2; }
tr:nth-child(even) { background: #EBF3FB; }
tr:nth-child(odd)  { background: #FFFFFF; }
.sdtm-annot  { color: #C00000; font-style: italic; font-weight: bold; font-size: 11px; }
.domain-tag  { display: inline-block; background: #2E75B6; color: white; padding: 2px 8px;
                border-radius: 10px; font-size: 11px; font-weight: bold; margin: 2px; }
.onco-tag    { display: inline-block; background: #375623; color: white; padding: 2px 8px;
                border-radius: 10px; font-size: 11px; font-weight: bold; margin: 2px; }
.visit-tag   { display: inline-block; background: #C55A11; color: white; padding: 2px 6px;
                border-radius: 3px; font-size: 11px; margin: 2px; }
.annot-key   { background: #FFF2CC; border: 1px solid #C00000; padding: 8px 12px;
                border-radius: 3px; font-size: 12px; margin-bottom: 12px; }
```

<div class="warn">
&#9888; FICTIONAL EDUCATIONAL DOCUMENT — NOT FOR REGULATORY USE<br>
This aCRF is part of a completely fictional Phase 3 NSCLC clinical trial simulation (SIMULATED-TORIVUMAB-2026).
All identifiers, drug names, and data are synthetic. Do NOT submit to any regulatory authority or clinical registry.
</div>

<div class="info">
<b>Study:</b> SIMULATED-TORIVUMAB-2026 &nbsp;|&nbsp; <b>Protocol:</b> TORIVA-LUNG 301 &nbsp;|&nbsp;
<b>Sponsor:</b> Celindra Therapeutics (fictional) &nbsp;|&nbsp; <b>Phase:</b> 3, randomised, double-blind, placebo-controlled<br>
<b>Indication:</b> Advanced/metastatic NSCLC — PD-L1 TPS &ge;50%, no sensitising EGFR/ALK &nbsp;|&nbsp;
<b>Treatment:</b> Torivumab 200 mg IV Q3W vs Placebo &nbsp;|&nbsp; <b>N:</b> 450 (2:1)<br>
<b>Primary Endpoint:</b> Overall Survival (OS) &nbsp;|&nbsp; <b>Response Criteria:</b> RECIST 1.1 (BICR)<br>
<b>Standards:</b> CDASH v2.1 &rarr; SDTMIG v3.4 &rarr; ADaMIG v1.3 | CDISC CT 2024-03 | MedDRA v27.0 | CTCAE v5.0
</div>

<div class="annot-key">
<b>Annotation Key:</b> <span class="sdtm-annot">&rarr; DOMAIN.VARIABLE [Codelist]</span>
&nbsp;&nbsp;&#8212;&nbsp;&nbsp;
SDTM annotations are shown in <span style="color:#C00000;font-weight:bold;">red</span> in the rightmost column of each form table.
Regulatory convention: red annotations indicate the target SDTM variable for each collected field.
</div>

---

# Visit Schedule

<span class="visit-tag">SCR Week -4</span>
<span class="visit-tag">C1D1 Baseline</span>
<span class="visit-tag">C1D8</span>
<span class="visit-tag">C1D15</span>
<span class="visit-tag">C1D22 EOC1</span>
<span class="visit-tag">Cycles 2&#8211;35 Q3W</span>
<span class="visit-tag">Imaging Q6W &rarr; Wk18</span>
<span class="visit-tag">Imaging Q12W</span>
<span class="visit-tag">EOT +30d</span>
<span class="visit-tag">FU-01 Mo3</span>
<span class="visit-tag">FU-02 Mo6</span>
<span class="visit-tag">FU-03 Mo12</span>
<span class="visit-tag">LTFU Q12W</span>

```{r visit-schedule}
visit_schedule <- read_csv("visit_schedule.csv", show_col_types = FALSE) %>%
  mutate(
    window     = ifelse(!is.na(window_early) & !is.na(window_late),
                        paste0(window_early, " / +", window_late, " ", window_unit),
                        paste0("\u00b1", window_late, " ", window_unit)),
    forms_required = gsub("\\|", ", ", forms_required)
  ) %>%
  select(visit_id, visit_name, epoch, scheduled_day, window, forms_required)

visit_schedule %>%
  kbl(col.names  = c("Visit ID", "Visit Name", "Epoch", "Day", "Window", "Forms Required"),
      booktabs   = TRUE) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    latex_options     = c("striped", "hold_position"),
    full_width        = TRUE, font_size = 11
  ) %>%
  html_row_spec(0, background = "#1F3864", color = "white", bold = TRUE)
```

---

# Forms Overview

<span class="domain-tag">DM</span>
<span class="domain-tag">DS</span>
<span class="domain-tag">IE</span>
<span class="domain-tag">EC</span>
<span class="domain-tag">DA</span>
<span class="domain-tag">AE</span>
<span class="domain-tag">CM</span>
<span class="domain-tag">MH</span>
<span class="domain-tag">SU</span>
<span class="domain-tag">VS</span>
<span class="domain-tag">LB</span>
<span class="domain-tag">PE</span>
<span class="domain-tag">DD</span>
&#8212; Foundational CDASH v2.1 Forms (13)

<span class="onco-tag">TU</span>
<span class="onco-tag">TR</span>
<span class="onco-tag">RS</span>
&#8212; Custom Oncology Forms &#8212; RECIST 1.1 (3)

---

# DM &#8212; Demographics

**CDASH:** DM &nbsp;|&nbsp; **SDTM:** DM &nbsp;|&nbsp; **ADaM:** ADSL &nbsp;|&nbsp;
**Visit:** Screening / Baseline

<div class="info">
Collects subject identification, date of birth, sex, race, ethnicity, and country.
USUBJID (system-derived as STUDYID-SITEID-SUBJID) is the primary key linking all SDTM domains.
AGE is auto-calculated from date of birth. ARM/ACTARM are assigned at randomisation and derived at SDTM level.
</div>

```{r dm}
render_form("DM")
```

---

# DS &#8212; Disposition

**CDASH:** DS &nbsp;|&nbsp; **SDTM:** DS &nbsp;|&nbsp; **ADaM:** ADSL, ADTTE &nbsp;|&nbsp;
**Visit:** Screening | C1D1 | EOT | FU01&#8211;FU03 | LTFU

<div class="info">
Captures protocol milestones and discontinuation reasons at every major decision point.
DSDECOD drives ADSL completion flags and ADTTE censoring rules.
DSSTDTC anchors the disposition date for each event.
</div>

```{r ds}
render_form("DS")
```

---

# IE &#8212; Inclusion / Exclusion Criteria

**CDASH:** IE &nbsp;|&nbsp; **SDTM:** IE &nbsp;|&nbsp; **ADaM:** ADSL &nbsp;|&nbsp;
**Visit:** Screening

<div class="info">
All inclusion criteria must be met (IEORRES = Y) and all exclusion criteria must be absent (IEORRES = N) before randomisation.
PD-L1 TPS &ge;50% (IN02), EGFR wild-type (IN03), and ALK negative (IN04) are mandatory eligibility gates.
IEORRES maps to IE.IEORRES; IETESTCD (e.g. IN01, EX01) maps to IE.IETESTCD.
</div>

```{r ie-fields}
render_form("IE")
```

**Eligibility Criteria Reference:**

```{r ie-criteria}
ie_criteria <- tibble::tibble(
  Code    = c("IN01","IN02","IN03","IN04","IN05","IN06","IN07","IN08","IN09","IN10",
              "EX01","EX02","EX03","EX04","EX05","EX06","EX07","EX08","EX09","EX10"),
  Cat     = c(rep("INCLUSION", 10), rep("EXCLUSION", 10)),
  Criterion = c(
    "Histologically confirmed NSCLC (Stage IIIB/IIIC/IV)",
    "PD-L1 TPS \u226550% by 22C3 pharmDx IHC (central lab)",
    "No sensitising EGFR mutations (exon 19 del, exon 21 L858R, other activating)",
    "No ALK gene rearrangement",
    "ECOG Performance Status 0 or 1",
    "Measurable disease per RECIST 1.1",
    "Age \u226518 years",
    "No prior systemic therapy for advanced/metastatic NSCLC",
    "Adequate organ function (haematology, hepatic, renal)",
    "Life expectancy \u226512 weeks",
    "Active autoimmune disease requiring systemic treatment",
    "Prior anti-PD-1 or anti-PD-L1 therapy",
    "Active (unstable) CNS metastases",
    "Active systemic corticosteroids >10 mg/day prednisone equivalent",
    "Active hepatitis B or C infection",
    "Known HIV (unless undetectable on ART)",
    "Other active malignancy within 2 years",
    "Pregnant or breastfeeding",
    "Prior organ or allogeneic bone marrow transplant",
    "Any condition interfering with study participation"
  ),
  Response = c(rep("Y required", 10), rep("N required", 10)),
  Annot   = c(rep("\u2192 IE.IEORRES [NY] / IE.IETESTCD", 20))
)

ie_criteria %>%
  kbl(col.names = c("Code", "Category", "Criterion", "Response", "SDTM Annotation"),
      booktabs = TRUE, escape = TRUE) %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    latex_options     = c("striped", "hold_position"),
    full_width        = TRUE, font_size = 11
  ) %>%
  html_row_spec(0, background = "#1F3864", color = "white", bold = TRUE) %>%
  {if (knitr::is_html_output())
    column_spec(., 5, color = "#C00000", bold = TRUE, italic = TRUE)
  else
    column_spec(., 5, color = "sdtmred", bold = TRUE, italic = TRUE)} %>%
  html_row_spec(1:10,  background = "#E2EFDA") %>%
  html_row_spec(11:20, background = "#FFF2CC")
```

---

# EC &#8212; Exposure as Collected

**CDASH:** EC &nbsp;|&nbsp; **SDTM:** EC (derived to EX) &nbsp;|&nbsp; **ADaM:** ADEX &nbsp;|&nbsp;
**Visit:** All on-treatment visits

<div class="info">
Captures actual dose administered per infusion visit. ECSTDTC / ECENDTC record infusion start and end times.
ECDOSEMOD + ECMODREAS capture dose modifications. EC domain is transformed to SDTM EX domain during SDTM derivation
(ECDOSE &rarr; EXDOSE; ECSTDTC &rarr; EXSTDTC). Treatment identity is blinded at collection; unblinded post-study.
</div>

```{r ec}
render_form("EC")
```

---

# DA &#8212; Drug Accountability

**CDASH:** DA &nbsp;|&nbsp; **SDTM:** DA &nbsp;|&nbsp; **ADaM:** ADEX &nbsp;|&nbsp;
**Visit:** C1D1 (Baseline) | EOT

<div class="info">
Records drug dispensed and returned at study start and end. DATEST distinguishes DISPENSED vs RETURNED records.
Used to calculate treatment duration and compliance. One record per accountability event.
</div>

```{r da}
render_form("DA")
```

---

# AE &#8212; Adverse Events

**CDASH:** AE &nbsp;|&nbsp; **SDTM:** AE &nbsp;|&nbsp; **ADaM:** ADAE &nbsp;|&nbsp;
**Coding:** MedDRA v27.0 | CTCAE v5.0 &nbsp;|&nbsp;
**Visit:** All on-treatment visits + Off-treatment FU

<div class="info">
Collected at every on-treatment and follow-up visit. AETERM is the verbatim investigator term; AEDECOD is coded centrally
by data management using MedDRA v27.0. CTCAE v5.0 grade recorded by investigator at worst severity. SAE expedited
reporting required within 24 hours (AESER = Y). AESERCR uses multi-select (up to 6 concurrent SAE criteria).
</div>

```{r ae}
render_form("AE")
```

---

# CM &#8212; Concomitant Medications

**CDASH:** CM &nbsp;|&nbsp; **SDTM:** CM &nbsp;|&nbsp; **ADaM:** ADCM &nbsp;|&nbsp;
**Visit:** Baseline + All on-treatment + FU visits

<div class="info">
Collects all prior and concomitant medications. CMTRT is the verbatim drug name; CMDECOD is coded centrally
using WHO Drug Dictionary. CMCAT distinguishes PRIOR (stopped before first dose) from CONCOMITANT (ongoing during study).
Partial start/end dates are acceptable (YYYY or YYYY-MM format).
</div>

```{r cm}
render_form("CM")
```

---

# MH &#8212; Medical History

**CDASH:** MH &nbsp;|&nbsp; **SDTM:** MH &nbsp;|&nbsp; **ADaM:** ADSL &nbsp;|&nbsp;
**Visit:** Screening | C1D1

<div class="info">
Captures prior medical conditions and oncology history including prior anticancer therapies.
MHCAT distinguishes ONCOLOGY HISTORY from GENERAL MEDICAL HISTORY.
MHSCAT subcategory enables identification of prior anticancer therapy, prior surgery, and prior radiation.
MHENRF records whether each condition was resolved (BEFORE) or ongoing (ONGOING) at study entry.
</div>

```{r mh}
render_form("MH")
```

---

# SU &#8212; Substance Use (Tobacco)

**CDASH:** SU &nbsp;|&nbsp; **SDTM:** SU &nbsp;|&nbsp; **ADaM:** ADSL &nbsp;|&nbsp;
**Visit:** Screening | C1D1

<div class="info">
Tobacco use history is clinically relevant for NSCLC. SUCAT is pre-filled as TOBACCO.
SUOCCUR flags ever-use. SUENRF distinguishes former (BEFORE) from current (ONGOING) smokers.
Pack-year history can be captured in SUPPSU if required by protocol.
</div>

```{r su}
render_form("SU")
```

---

# VS &#8212; Vital Signs

**CDASH:** VS &nbsp;|&nbsp; **SDTM:** VS &nbsp;|&nbsp; **ADaM:** ADVS &nbsp;|&nbsp;
**Visit:** All visits

<div class="info">
Horizontal format: one row per vital sign per visit. VSTESTCD and VSTEST are pre-populated per row (read-only).
VSPOS (position) is required for blood pressure measurements. HEIGHT and BSA are collected at Screening only.
Body weight collected at all visits for dose-modification decisions.
</div>

```{r vs}
render_form("VS")
```

**Vital Sign Test Panel:**

```{r vs-panel}
vs_panel <- tibble::tibble(
  VSTESTCD = c("SYSBP","DIABP","PULSE","TEMP","RESP","WEIGHT","HEIGHT","BSA"),
  Test     = c("Systolic Blood Pressure","Diastolic Blood Pressure","Pulse Rate",
               "Temperature","Respiratory Rate","Body Weight","Body Height","Body Surface Area"),
  Units    = c("mmHg","mmHg","beats/min","degrees C","breaths/min","kg","cm","m\u00b2"),
  Range    = c("60\u2013250","40\u2013150","30\u2013200","34.0\u201342.0","6\u201340",
               "30\u2013250","100\u2013220","Mosteller formula"),
  Visits   = c("All","All","All","All","All","All","Screening only","Screening only"),
  Annot    = rep("\u2192 VS.VSORRES [VS_TEST]", 8)
)

vs_panel %>%
  kbl(col.names = c("VSTESTCD","Test Name","Units","Normal Range","Visit(s)","SDTM Annotation"),
      booktabs = TRUE, escape = TRUE) %>%
  kable_styling(
    bootstrap_options = c("striped","hover","condensed"),
    latex_options     = c("striped","hold_position"),
    full_width = TRUE, font_size = 11
  ) %>%
  html_row_spec(0, background = "#1F3864", color = "white", bold = TRUE) %>%
  {if (knitr::is_html_output())
    column_spec(., 6, color = "#C00000", bold = TRUE, italic = TRUE)
  else
    column_spec(., 6, color = "sdtmred", bold = TRUE, italic = TRUE)}
```

---

# LB &#8212; Laboratory Test Results

**CDASH:** LB &nbsp;|&nbsp; **SDTM:** LB &nbsp;|&nbsp; **ADaM:** ADLB &nbsp;|&nbsp;
**Visit:** Screening | C1D1 | C1D22 | C2D22 | CxD22 | EOT

<div class="info">
Two panels on the LB form: (1) <b>Clinical labs</b> &#8212; haematology, chemistry, urinalysis collected at all lab visits;
(2) <b>Baseline biomarkers</b> &#8212; molecular profiling panel collected at Screening/C1D1 only.
LBCAT will distinguish panels in SDTM (CHEMISTRY / HAEMATOLOGY / URINALYSIS / BIOMARKER).
LBNRIND (LOW/NORMAL/HIGH) is system-derived from reference ranges. LBCLSIG requires investigator sign-off for abnormals.
</div>

## LB &#8212; Field Structure

```{r lb-fields}
render_form("LB", "Laboratory Test Results")
```

## LB &#8212; Clinical Laboratory Panel

```{r lb-clinical}
lb_clinical <- tibble::tibble(
  LBTESTCD = c("HGB","WBC","NEUT","LYMPH","PLT",
               "ALT","AST","ALKPH","BILI","CREAT","SODIUM","POTASS","ALBUMIN","TSH","GLUC",
               "USPECGR","UPH","UPROT","UGLUC","UBILI","UKET","UBLOOD","UNITRITE","ULEUK"),
  Test     = c("Haemoglobin","White Blood Cell Count","Neutrophils (Abs)","Lymphocytes (Abs)","Platelet Count",
               "Alanine Aminotransferase","Aspartate Aminotransferase","Alkaline Phosphatase",
               "Total Bilirubin","Creatinine","Sodium","Potassium","Albumin",
               "Thyroid Stimulating Hormone","Glucose (Fasting)",
               "Urine Specific Gravity","Urine pH","Urine Protein","Urine Glucose","Urine Bilirubin",
               "Urine Ketones","Urine Blood","Urine Nitrites","Urine Leukocyte Esterase"),
  Panel    = c(rep("Haematology",5), rep("Chemistry",10), rep("Urinalysis",9)),
  Units    = c("g/dL","10\u2079/L","10\u2079/L","10\u2079/L","10\u2079/L",
               "U/L","U/L","U/L","umol/L","umol/L","mmol/L","mmol/L","g/L","mIU/L","mmol/L",
               "none","none","mg/dL","mmol/L","grade","grade","grade","grade","grade"),
  NormalRange = c("M:13.5\u201317.5 / F:12.0\u201316.0","4.0\u201311.0","1.8\u20137.5",
                  "1.0\u20134.8","150\u2013400","7\u201356","10\u201340","44\u2013147",
                  "3.4\u201320.5","M:53\u2013115 / F:44\u201397","136\u2013145","3.5\u20135.1",
                  "35\u201350","0.4\u20134.0","3.9\u20136.1",
                  "1.003\u20131.030","4.5\u20138.0","Negative","Negative","Negative",
                  "Negative","Negative","Negative","Negative"),
  Annot    = rep("\u2192 LB.LBORRES [LB_TEST]", 24)
)

lb_clinical %>%
  kbl(col.names = c("LBTESTCD","Test Name","Panel","Units","Normal Range","SDTM Annotation"),
      booktabs = TRUE, escape = TRUE) %>%
  kable_styling(
    bootstrap_options = c("striped","hover","condensed"),
    latex_options     = c("striped","hold_position"),
    full_width = TRUE, font_size = 11
  ) %>%
  html_row_spec(0, background = "#1F3864", color = "white", bold = TRUE) %>%
  {if (knitr::is_html_output())
    column_spec(., 6, color = "#C00000", bold = TRUE, italic = TRUE)
  else
    column_spec(., 6, color = "sdtmred", bold = TRUE, italic = TRUE)} %>%
  pack_rows("Haematology", 1, 5,  bold = TRUE,
            label_row_css = if (knitr::is_html_output()) "background:#DEEAF1;font-weight:bold;" else "") %>%
  pack_rows("Chemistry",   6, 15, bold = TRUE,
            label_row_css = if (knitr::is_html_output()) "background:#DEEAF1;font-weight:bold;" else "") %>%
  pack_rows("Urinalysis", 16, 24, bold = TRUE,
            label_row_css = if (knitr::is_html_output()) "background:#E2EFDA;font-weight:bold;" else "")
```

## LB &#8212; Baseline Biomarker Panel (Screening / C1D1 only)

```{r lb-biomarker-fields}
render_form("LB", "Laboratory Test Results (Biomarkers)")
```

```{r lb-biomarker-panel}
lb_bio <- tibble::tibble(
  LBTESTCD = c("PD-L1_TPS","EGFR_MUT","ALK_REARR","ROS1_REARR","KRAS_G12C",
               "MET_EX14","RET_REARR","BRAF_V600E","NTRK_FUSE","TMB"),
  Test     = c("PD-L1 Tumour Proportion Score","EGFR Mutation Status","ALK Rearrangement",
               "ROS1 Rearrangement","KRAS G12C Mutation","MET Exon 14 Skipping",
               "RET Rearrangement","BRAF V600E Mutation","NTRK Gene Fusion",
               "Tumour Mutational Burden"),
  ResultType = c("Numeric 0\u2013100%","Codelist","Codelist","Codelist","Codelist",
                 "Codelist","Codelist","Codelist","Codelist","Numeric (mut/Mb)"),
  Eligibility = c("\u226550% REQUIRED","Absence REQUIRED","Absence REQUIRED",
                  "Not exclusion","Not exclusion","Not exclusion",
                  "Not exclusion","Not exclusion","Not exclusion","Exploratory"),
  Method   = c("IHC (22C3 pharmDx)","NGS / PCR","FISH / IHC","FISH","NGS / PCR",
               "NGS","FISH / NGS","NGS / PCR","FISH / NGS","NGS"),
  Annot    = rep("\u2192 LB.LBORRES / LB.LBSTRESC [LB_BIOMARKER]", 10)
)

lb_bio %>%
  kbl(col.names = c("LBTESTCD","Test Name","Result Type","Eligibility","Method","SDTM Annotation"),
      booktabs = TRUE, escape = TRUE) %>%
  kable_styling(
    bootstrap_options = c("striped","hover","condensed"),
    latex_options     = c("striped","hold_position"),
    full_width = TRUE, font_size = 11
  ) %>%
  html_row_spec(0, background = "#1F3864", color = "white", bold = TRUE) %>%
  {if (knitr::is_html_output())
    column_spec(., 6, color = "#C00000", bold = TRUE, italic = TRUE)
  else
    column_spec(., 6, color = "sdtmred", bold = TRUE, italic = TRUE)} %>%
  html_row_spec(1:3, background = "#FFF2CC")
```

*Biomarker result categories:* POSITIVE / NEGATIVE / NOT TESTED / UNKNOWN. PD-L1 TPS additionally mapped to &ge;50% or &lt;50% for eligibility.

---

# PE &#8212; Physical Examination

**CDASH:** PE &nbsp;|&nbsp; **SDTM:** PE &nbsp;|&nbsp; **ADaM:** ADSL &nbsp;|&nbsp;
**Visit:** Screening | C1D1 | EOT

<div class="info">
System-by-system physical examination. PESTRESC classifies findings as NORMAL, ABNORMAL NCS (not clinically significant),
or ABNORMAL CS (clinically significant). ECOG Performance Status (0&#8211;4) is captured as a PE finding
(PETEST = ECOG PS; PEORRES = 0/1/2/3/4) &#8212; must be 0 or 1 at screening for eligibility.
</div>

```{r pe}
render_form("PE")
```

**PE Body Systems:**

```{r pe-systems}
pe_sys <- tibble::tibble(
  System = c("GENERAL APPEARANCE","RESPIRATORY","CARDIOVASCULAR","GASTROINTESTINAL",
             "NEUROLOGICAL","DERMATOLOGICAL","MUSCULOSKELETAL","LYMPH NODES","ECOG PS"),
  Note   = c("Overall appearance","Primary disease site","Cardiovascular status",
             "GI assessment","Neurological status","Immune-related AE monitoring (rash)",
             "Musculoskeletal function","NSCLC nodal assessment","0\u20134 scale; eligibility 0\u20131"),
  Annot  = rep("\u2192 PE.PETEST [PE_TEST] / PE.PEORRES [PE_RESULT / ECOG]", 9)
)
pe_sys %>%
  kbl(col.names = c("Body System (PETEST)", "Clinical Relevance", "SDTM Annotation"),
      booktabs = TRUE, escape = TRUE) %>%
  kable_styling(bootstrap_options = c("striped","hover","condensed"),
                latex_options     = c("striped","hold_position"),
                full_width = TRUE, font_size = 11) %>%
  html_row_spec(0, background = "#1F3864", color = "white", bold = TRUE) %>%
  {if (knitr::is_html_output())
    column_spec(., 3, color = "#C00000", bold = TRUE, italic = TRUE)
  else
    column_spec(., 3, color = "sdtmred", bold = TRUE, italic = TRUE)}
```

---

# DD &#8212; Death Details

**CDASH:** DD &nbsp;|&nbsp; **SDTM:** DD &nbsp;|&nbsp; **ADaM:** ADTTE &nbsp;|&nbsp;
**Visit:** Post-mortem (unscheduled) &#8212; complete if subject dies on-study or within follow-up

<div class="info">
DDDTC (date of death) drives ADTTE OS derivation (CNSR = 0; AVAL = time from randomisation to death).
Multiple DDORRES records capture different aspects of death (primary cause, contributing cause, autopsy,
relationship to study drug) &#8212; each distinguished by DDTESTCD in SDTM.
</div>

```{r dd}
render_form("DD")
```

---

# TU &#8212; Tumour Identification

**CDASH:** TU &nbsp;|&nbsp; **SDTM:** TU &nbsp;|&nbsp; **ADaM:** ADTR &nbsp;|&nbsp;
**Visit:** Baseline Imaging (IMG01)

<div class="recist">
<b>RECIST 1.1 Lesion Selection Rules:</b>
TARGET lesions: measurable &#8805;10 mm longest diameter (&#8805;15 mm short axis for lymph nodes);
maximum 5 target lesions total; maximum 2 per organ; must be reproducibly measurable by CT/MRI.
NON-TARGET: all other lesions including bone lesions, pleural effusions, ascites.
All baseline lesions must be documented. Baseline TU records are linked to all subsequent TR records via TRLNKID = TUSEQ.
</div>

```{r tu}
render_form("TU")
```

---

# TR &#8212; Tumour Results (Lesion Measurements)

**CDASH:** TR &nbsp;|&nbsp; **SDTM:** TR &nbsp;|&nbsp; **ADaM:** ADTR &nbsp;|&nbsp;
**Visit:** All imaging visits &#8212; Q6W (Wk 6, 12, 18) then Q12W

<div class="info">
One record per lesion per imaging visit. TRLNKID references baseline TUSEQ. LDIAM (longest diameter) is the primary
RECIST 1.1 measurement for target lesions. LPERP (perpendicular / short axis) is used for lymph node measurements.
Sum of Longest Diameters (SLD) and % change from baseline are derived in ADaM (ADTR).
TRORRES = 0 mm indicates complete resolution of a target lesion.
</div>

```{r tr}
render_form("TR")
```

---

# RS &#8212; Disease Response (Overall Assessment)

**CDASH:** RS &nbsp;|&nbsp; **SDTM:** RS &nbsp;|&nbsp; **ADaM:** ADRS &nbsp;|&nbsp;
**Visit:** All imaging visits &#8212; Q6W (Wk 6, 12, 18) then Q12W

<div class="recist">
<b>RECIST 1.1 Overall Response Definitions:</b><br>
<b>CR</b> = Complete Response: disappearance of all target lesions; all lymph nodes &lt;10 mm short axis.<br>
<b>PR</b> = Partial Response: &#8805;30% decrease in SLD from baseline nadir.<br>
<b>SD</b> = Stable Disease: neither sufficient shrinkage for PR nor sufficient increase for PD.<br>
<b>PD</b> = Progressive Disease: &#8805;20% increase in SLD with &#8805;5 mm absolute increase; OR new lesions (RSNEWLES = Y).<br>
<b>NE</b> = Not Evaluable: unable to determine response; reason must be documented.<br>
Primary regulatory submission uses BICR (RSEVAL = INDEPENDENT ASSESSOR). Investigator response collected in parallel.
</div>

```{r rs}
render_form("RS")
```

---

# Traceability Summary

<div class="info">
The table below summarises the complete CRF &rarr; SDTM &rarr; ADaM traceability chain across all 16 forms.
SDTM domains and ADaM datasets follow SDTMIG v3.4 and ADaMIG v1.3 respectively.
</div>

```{r traceability}
trace <- tibble::tibble(
  Form         = c("Demographics","Disposition","Inclusion/Exclusion","Exposure as Collected",
                   "Drug Accountability","Adverse Events","Concomitant Medications",
                   "Medical History","Substance Use","Vital Signs",
                   "Lab Results \u2014 Clinical","Lab Results \u2014 Biomarkers",
                   "Physical Examination","Death Details",
                   "Tumour Identification","Tumour Results","Disease Response"),
  CDASH        = c("DM","DS","IE","EC","DA","AE","CM","MH","SU","VS","LB","LB","PE","DD","TU","TR","RS"),
  SDTM         = c("DM","DS","IE","EC \u2192 EX","DA","AE","CM","MH","SU","VS","LB","LB","PE","DD","TU","TR","RS"),
  ADaM         = c("ADSL","ADSL, ADTTE","ADSL","ADEX","ADEX","ADAE","ADCM","ADSL","ADSL",
                   "ADVS","ADLB","ADLB","ADSL","ADTTE","ADTR","ADTR","ADRS"),
  KeyDerivations = c(
    "USUBJID key; ARM/ACTARM; AGE; SEX; RACE",
    "EOSSTT; DCSREAS; ADSL completion/censoring flags",
    "ITTFL; SAFFL; eligibility population flags",
    "TRTSDT/DT; TRTEDTM; AVAL cumulative dose; compliance",
    "TRTDUR; drug accountability reconciliation",
    "AESEQ; treatment-related flag; AESERD; grade flags; ANL01FL",
    "CMDOSE; CMSTDY; CMSEQ; prior/concomitant split",
    "NHISTFL; prior anticancer therapy flags",
    "SMOKFL; smoking status; pack-year history (SUPPSU)",
    "AVAL; AVALC; BASE; CHG; PCHG; shift tables",
    "AVAL; ANRLO/HI; shift; toxicity grade flags; ANL01FL",
    "PD-L1 \u226550% flag; biomarker subgroup flags (KRAS, TMB)",
    "ECOGFL; ECOG at baseline; ECOG change",
    "CNSR=0; AVAL for OS derivation in ADTTE",
    "Baseline SLD; lesion-level linking via RELREC",
    "SLD; PCHG; nadir; BOR logic; ADTR AVAL",
    "BOR; DoR; TTR; ORR; BICR vs investigator responses"
  )
)

trace %>%
  kbl(col.names = c("CRF Form","CDASH","SDTM","ADaM","Key Derivations"),
      booktabs = TRUE, escape = TRUE) %>%
  kable_styling(
    bootstrap_options = c("striped","hover","condensed"),
    latex_options     = c("striped","hold_position"),
    full_width = TRUE, font_size = 11
  ) %>%
  html_row_spec(0, background = "#1F3864", color = "white", bold = TRUE) %>%
  {if (knitr::is_html_output()) {
    column_spec(., 3, color = "#C00000", bold = TRUE) %>%
    column_spec(4, color = "#2E75B6", bold = TRUE)
  } else {
    column_spec(., 3, color = "sdtmred", bold = TRUE) %>%
    column_spec(4, bold = TRUE)
  }} %>%
  pack_rows("Foundational CDASH Forms (13)",  1, 14, bold = TRUE,
            label_row_css = if (knitr::is_html_output()) "background:#DEEAF1;font-weight:bold;" else "") %>%
  pack_rows("Custom Oncology Forms (3)",      15, 17, bold = TRUE,
            label_row_css = if (knitr::is_html_output()) "background:#E2EFDA;font-weight:bold;" else "")
```

---

*End of Annotated CRF &#8212; SIMULATED-TORIVUMAB-2026*

*Phase 2 deliverable &#8212; Gate 2 Review.*

*Standards: CDASH v2.1 | SDTMIG v3.4 | ADaMIG v1.3 | CDISC CT 2024-03 | MedDRA v27.0 | CTCAE v5.0 | RECIST 1.1*

*&#9888; FICTIONAL EDUCATIONAL DOCUMENT &#8212; NOT FOR REGULATORY USE*
